% How to acknowledge folks

%I consider myself a man of few words.

I want to express my most sincere gratitude to Dr. Jianzhong Su for his encouragement and support when I was unsure of myself, making it possible for me to succeed eventually.

I also want to extend my gratitude to the members of my dissertation committee: Dr. Hristo V. Kojouharov, Dr. Ren-Cang Li, and Dr. Li Wang (in alphabetical order).
%
Thanks for your continuous support and guidance during my time at UTA.

Thanks to Imelda Trejo-Lorenzo for encouraging, helping, and guiding me to pursue a PhD at an outstanding university in the USA.

I want to thank the colleagues I met at UTA for their company and moral support: Miguel A., Zachary V., Dwight W., Saber A., Saul C., Hrishabh K., Kiran M., Talon J., Amanda P., John M., Crystal M., Mondal Z., Oscar A., Madhu G., Zachary C., Jose L., Amairani S., Angela A., Kitham A., among many more.
%
A comprehensive list of the friends who improved my life is an extensive task, and it is beyond the scope of this paragraph.
%
I hope my presence was not a significant burden to y'all.

I want to mention my friends from home who are family in my heart: Omar C., Augusto T., Suri R., Berenice R., Jesus R., Valeria R., Ismael A., 
Maricela Z, Susana B., among others.
%
Thanks for your friendship.

%Finally, I want to dedicate this accomplishment to my entire biological family: my mother, Maria Guadalupe Alva-Gonzalez, my brother, Erick Ricardo Enciso-Alva, and my late father, Nicolas Enciso-Maturano.
%
%Despite the harsh times, we could stay afloat and continue.
%
%This is the way.